Landscape composition and beneficial insects

### 2020-05-27 manuscript/manuscript_outline.Rmd
Added refs. Tried out appendix section (somewhat successful)

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, et al."
date: "Spring 2020"
output: bookdown::html_document2 
bibliography: refs.bib
csl: ecology-letters.csl
---

@@

```{r varComp, echo=FALSE, fig.cap='\\label{fig:varComp} Variance components of all models'}
ggplot(varComp,aes(x=term,y=std.dev))+geom_col()+theme_classic()+facet_wrap(~spp,ncol=1,scales='free_y')+
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

@@

* Lemme tell ya 
  + We found all kinds of stuff
  + Boy oh boy is it cool

>>>>

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, et al."
date: "Spring 2020"
bibliography: refs.bib
csl: ecology-letters.csl
output:
  bookdown::html_document2:
    pandoc_args: ["--include-after-body=manuscript_appendix.md"]
---

@@

@@

* Pterostichus responded to landscape composition
